---
title: "Data Cleaning"
author: "Andy"
date: "September 26, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This scripts aims at cleaning the original dataset that we have and exporting a clean csv for our analysis.

What has been done ?
1) merging crime_data and code_data into one single dataset
2) date formating and creation of column with day/month/year
3) remove year 2017 because incomplete
4) Label victim.descent and create a more global victim.descent.global with fewer categories
5) columns longitude and latitude created from location 

## Import and merge dataset

```{r library, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(ggmap)
library(ggplot2)
library(dplyr)
library(lubridate)
library(tidyr)
library(stringr)
```

```{r import, echo=TRUE}
crime_data <- read.csv("data/Crime_Data_2010_2017.csv")
#code_data <- read.csv("data/MO_Codes.csv")

#crime_data <- merge(crime_data, code_data, by.x = "Crime.Code.1", by.y = "MO_Code", all.x = TRUE)
```

## Description of the dataset

You can also embed plots, for example:

```{r description, echo=FALSE}
head(crime_data)
str(crime_data)
```

## Data cleaning

# Dates and Time
```{r}
# Convert date format

time_func <- function(timestamp) {
  timestamp <- as.character(timestamp)
  while(nchar(timestamp) < 4) {
    timestamp <- paste("0", timestamp, sep = '')
    } 
  return(timestamp)
}

crime_data$Time.Occurred <- sapply(crime_data$Time.Occurred, time_func)
crime_data$Time.Occurred.C <- as.POSIXct(paste(as.character(crime_data$Date.Occurred), as.character(crime_data$Time.Occurred)), format="%m/%d/%Y %H%M")

crime_data$Date.Reported.C <- as.Date(crime_data$Date.Reported, format=("%m/%d/%Y"))
crime_data$Date.Occurred.C <- as.Date(crime_data$Date.Occurred, format=("%m/%d/%Y"))

crime_data <- separate(crime_data, col=Date.Occurred, into=c('Day.Occurred','Month.Occurred', "Year.Occurred"), sep="/")
crime_data <- separate(crime_data, col=Date.Reported, into=c('Day.Reported','Month.Reported', "Year.Reported"), sep="/")

# Create column time_between_occurred_reported
crime_data$Time.Between.Occured.Reported <- crime_data$Date.Reported.C - crime_data$Date.Occurred.C

time_func <- function(numb){
  if(numb <3){return("less than 3 days")
  } else if(numb >=3 & numb < 10 ){return("3 days to 10 days")
    } else if(numb >=10 & numb < 15 ){return("10 days to 15 days")
    } else if(numb >= 15) {return("more than 15 days")}
}

crime_data$Time.Between.Occured.Reported.Global = sapply(crime_data$Time.Between.Occured.Reported, time_func)


time_func2 <- function(numb){
  if(numb >=700 & numb<=1200){return("7am to noon")
  } else if(numb >=1200 & numb < 1800 ){return("noon to 6pm")
  } else if(numb >=1800 & numb <2400 ){return("6pm to midnight")
  } else if(numb >= 0 & numb<700) {return("midnight to 7am")}
}

crime_data$Time.Occurred.Global = sapply(crime_data$Time.Occurred, time_func2)
```

# Add new variable for status description

```{r}
#categorize the Status Description in to 3 type: Arrested,invest cont and other
levels(crime_data$Status.Description)[levels(crime_data$Status.Description)=="Adult Arrest"] <- "Arrested"
levels(crime_data$Status.Description)[levels(crime_data$Status.Description)=="Juv Arrest"] <- "Arrested"
levels(crime_data$Status.Description)[levels(crime_data$Status.Description)=="Juv Other"] <- "Other"
levels(crime_data$Status.Description)[levels(crime_data$Status.Description)=="Adult Other"] <- "Other"
levels(crime_data$Status.Description)[levels(crime_data$Status.Description)=="UNK"] <- "Other"
```

# Filter

Remove year 2017 (incomplete)
```{r filter_year}
crime_data <- crime_data %>% filter(Year.Occurred < 2017)
```

# Labels

```{r label}

# Victim Descent more global
crime_data[, "Victim.Descent.Global"] <- sapply(crime_data[, "Victim.Descent"], as.character)
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "W", "White")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "B", "Black")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "H", "Hispanic")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "A", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "C", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "J", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "K", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "F", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "C", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "L", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "D", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "V", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "Z", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "O", "Others")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "G", "Others")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "X", "Others")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "I", "Others")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "P", "Pacific Islander")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "S", "Pacific Islander")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "U", "Pacific Islander")
crime_data[, "Victim.Descent.Global"] <- sapply(crime_data[, "Victim.Descent.Global"], as.factor)

# Label Victim.Descent
crime_data$Victim.Descent <- factor(crime_data[, "Victim.Descent"], levels = c("H", "W", "B", "O", "A", "C", "", "X", "F", "U", "K", "P", "G", "J", "I", "V", "Z", "S", "D", "L", "-"), labels = c("Hispanic", "White", "Black", "Other", "Other Asian", "Chinese", "", "Unknown", "Filipino", "Hawaiian", "Korean", "Pacific Islander", "Guamanian", "Japanese", "American Indian/Alaskan Native", "Vietnamese", "Asian Indian", "Samoan", "Cambodian", "Laotian", "-")) 

```

# Longitude and lattitude

```{r}
crime_data[, "Location"] <- sapply(crime_data[, "Location"], as.character)

lat_func <- function(location) {return(as.numeric(str_sub(strsplit(location, split = ",")[[1]], 2, -1)[1]))}
long_func <- function(location) {return(as.numeric(str_sub(strsplit(location, split = ",")[[1]], 1, -2)[2]))}


crime_data$longitude <- sapply(crime_data$Location, long_func)
crime_data$lattitude <- sapply(crime_data$Location, lat_func)
```

# Rename Crime variables 

```{r}

# Create Code Type Data Dataframe
crime_code <- 100:956
crime_type <- c(rep("Homicide", 11), 
                    rep("Others", 9), 
                    rep("Rape", 11),
                    rep("Others", 79),
                    rep("Robbery", 6),
                    rep("Others", 14),
                    rep("Assault", 7),
                    rep("Others", 13),
                    rep("Gunshots Fired", 2),
                    rep("Others", 58),
                    rep("Burglary/Theft", 161),
                    rep("Others", 9),
                    rep("Vehicle Theft", 121),
                    rep("Others", 21),
                    rep("Battery", 6),
                    rep("Others", 20),
                    rep("Arson", 2),
                    rep("Others", 4),
                    rep("Counterfeit/Fraud", 9),
                    rep("Burglary/Theft", 3),
                    rep("Counterfeit/Fraud", 5),
                    rep("Others", 69),
                    rep("Vandalism", 6),
                    rep("Others", 7),
                    rep("Gunshots Fired",9),
                    rep("Other Sexual Offences", 2),
                    rep("Others", 41),
                    rep("Other Sexual Offences", 6),
                    rep("Others", 4),
                    rep("Other Sexual Offences", 46),
                    rep("Drug Offences", 5),
                    rep("Others", 34),
                    rep("Contempt of Court", 4),
                    rep("Others", 6),
                    rep("Kidnapping", 13),
                    rep("Vandalism", 2),
                    rep("Others", 7),
                    rep("Other Sexual Offences", 2),
                    rep("Others", 6),
                    rep("Counterfeit/Fraud", 3),
                    rep("Others", 8),
                    rep("Counterfeit/Fraud", 2),
                    rep("Others", 2),
                    rep("Other Sexual Offences", 2))

crime_type_data <- data.frame(crime_code, crime_type)

crime_data <- merge(crime_data, crime_type_data, by.x = "Crime.Code", by.y = "crime_code", all.x = TRUE)
```


```{r}
#identify public holidays

LA_holiday <- c(as.Date("2017-09-04"),
                as.Date("2017-07-04"),
                as.Date("2017-05-29"),
                as.Date("2017-03-27"),
                as.Date("2017-02-20"),
                as.Date("2017-01-30"),
                as.Date("2017-01-16"),
                as.Date("2017-01-02"),
                as.Date("2017-01-01"),
                as.Date("2016-12-26"),
                as.Date("2016-11-25"),
                as.Date("2016-11-24"),
                as.Date("2016-11-11"),
                as.Date("2016-09-05"),
                as.Date("2016-07-04"),
                as.Date("2016-05-30"),
                as.Date("2016-02-15"),
                as.Date("2016-01-30"),
                as.Date("2016-01-18"),
                as.Date("2016-01-01"),
                as.Date("2015-12-25"),
                as.Date("2015-11-27"),
                as.Date("2015-11-26"),
                as.Date("2015-11-11"),
                as.Date("2015-09-07"),
                as.Date("2015-07-03"),
                as.Date("2015-05-25"),
                as.Date("2015-03-31"),
                as.Date("2015-02-16"),
                as.Date("2015-01-30"),
                as.Date("2015-01-19"),
                as.Date("2015-01-01"),
                as.Date("2014-12-25"),
                as.Date("2014-11-28"),
                as.Date("2014-11-27"),
                as.Date("2014-11-11"),
                as.Date("2014-10-13"),
                as.Date("2014-09-01"),
                as.Date("2014-07-04"),
                as.Date("2014-05-26"),
                as.Date("2014-03-31"),
                as.Date("2014-02-17"),
                as.Date("2014-01-01"),
                as.Date("2013-12-25"),
                as.Date("2013-11-28"),
                as.Date("2013-11-11"),
                as.Date("2013-10-14"),
                as.Date("2013-09-02"),
                as.Date("2013-07-04"),
                as.Date("2013-05-27"),
                as.Date("2013-02-18"),
                as.Date("2013-01-21"),
                as.Date("2013-01-01"),
                as.Date("2012-12-25"),
                as.Date("2012-11-23"),
                as.Date("2012-11-22"),
                as.Date("2012-11-12"),
                as.Date("2012-10-08"),
                as.Date("2012-09-03"),
                as.Date("2012-07-04"),
                as.Date("2012-05-28"),
                as.Date("2012-02-20"),
                as.Date("2012-01-16"),
                as.Date("2012-01-02"),
                as.Date("2011-12-26"),
                as.Date("2011-11-25"),
                as.Date("2011-11-24"),
                as.Date("2011-11-11"),
                as.Date("2011-10-10"),
                as.Date("2011-07-04"),
                as.Date("2011-05-30"),
                as.Date("2011-02-21"),
                as.Date("2011-01-17"),
                as.Date("2010-12-31"),
                as.Date("2010-12-24"),
                as.Date("2010-11-26"),
                as.Date("2010-11-25"),
                as.Date("2010-11-11"),
                as.Date("2010-10-11"),
                as.Date("2010-09-06"),
                as.Date("2010-07-05"),
                as.Date("2010-05-31"),
                as.Date("2010-02-15"),
                as.Date("2010-01-18"),
                as.Date("2010-01-01"))

all_Sundays <- seq(from=date("2010-01-03"),to=date("2016-12-31"),by=7)

Sunday_PH <- unique(append(LA_holiday,all_Sundays))


crime_data <- mutate(crime_data,public_holiday=ifelse(Date.Occurred.C %in% LA_holiday,TRUE,FALSE))
crime_data <- mutate(crime_data,Sundays_public_holiday=ifelse(Date.Occurred.C %in% Sunday_PH,TRUE,FALSE))
crime_data <- mutate(crime_data,Sundays=ifelse(Date.Occurred.C %in% all_Sundays,TRUE,FALSE))

                
```




## Export dataset

```{r}
write.csv(crime_data, "data/clean_data.csv")
```
