---
title: "Data Cleaning"
author: "Andy"
date: "September 26, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This scripts aims at cleaning the original dataset that we have and exporting a clean csv for our analysis.

What has been done ?
1) merging crime_data and code_data into one single dataset
2) date formating and creation of column with day/month/year
3) remove year 2017 because incomplete
4) Label victim.descent and create a more global victim.descent.global with fewer categories
5) columns longitude and latitude created from location 

## Import and merge dataset

```{r library, echo=FALSE, warning=FALSE}
library(dplyr)
library(ggmap)
library(ggplot2)
library(dplyr)
library(lubridate)
library(tidyr)
library(stringr)
```

```{r import, echo=TRUE}
crime_data <- read.csv("data/Crime_Data_2010_2017.csv")
code_data <- read.csv("data/MO_Codes.csv")

crime_data <- merge(crime_data, code_data, by.x = "Crime.Code.1", by.y = "MO_Code", all.x = TRUE)
```

## Description of the dataset

You can also embed plots, for example:

```{r description, echo=FALSE}
head(crime_data)
str(crime_data)
```

## Data cleaning

# Dates and Time
```{r}
# Convert date format

time_func <- function(timestamp) {
  timestamp <- as.character(timestamp)
  while(nchar(timestamp) < 4) {
    timestamp <- paste("0", timestamp, sep = '')
    } 
  return(timestamp)
}

crime_data$Time.Occurred <- sapply(crime_data$Time.Occurred, time_func)
crime_data$Time.Occurred.C <- as.POSIXct(paste(as.character(crime_data$Date.Occurred), as.character(crime_data$Time.Occurred)), format="%m/%d/%Y %H%M")

crime_data$Date.Reported.C <- as.Date(crime_data$Date.Reported, format=("%m/%d/%Y"))
crime_data$Date.Occurred.C <- as.Date(crime_data$Date.Occurred, format=("%m/%d/%Y"))

crime_data <- separate(crime_data, col=Date.Occurred, into=c('Day.Occurred','Month.Occurred', "Year.Occurred"), sep="/")
crime_data <- separate(crime_data, col=Date.Reported, into=c('Day.Reported','Month.Reported', "Year.Reported"), sep="/")

# Create column time_between_occurred_reported
crime_data$Time.Between.Occured.Reported <- crime_data$Date.Reported.C - crime_data$Date.Occurred.C
```

# Filter

Remove year 2017 (incomplete)
```{r filter_year}
crime_data <- crime_data %>% filter(Year.Occurred < 2017)
```

# Labels

```{r label}

# Victim Descent more global
crime_data[, "Victim.Descent.Global"] <- sapply(crime_data[, "Victim.Descent"], as.character)
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "W", "White")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "B", "Black")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "H", "Hispanic")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "A", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "C", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "J", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "K", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "F", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "C", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "L", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "D", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "V", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "Z", "Asian")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "O", "Others")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "G", "Others")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "X", "Others")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "I", "Others")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "P", "Pacific Islander")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "S", "Pacific Islander")
crime_data$Victim.Descent.Global <- str_replace(crime_data$Victim.Descent.Global, "U", "Pacific Islander")
crime_data[, "Victim.Descent.Global"] <- sapply(crime_data[, "Victim.Descent.Global"], as.factor)

# Label Victim.Descent
crime_data$Victim.Descent <- factor(crime_data[, "Victim.Descent"], levels = c("H", "W", "B", "O", "A", "C", "", "X", "F", "U", "K", "P", "G", "J", "I", "V", "Z", "S", "D", "L", "-"), labels = c("Hispanic", "White", "Black", "Other", "Other Asian", "Chinese", "", "Unknown", "Filipino", "Hawaiian", "Korean", "Pacific Islander", "Guamanian", "Japanese", "American Indian/Alaskan Native", "Vietnamese", "Asian Indian", "Samoan", "Cambodian", "Laotian", "-")) 

```

# Longitude and lattitude

```{r}
crime_data[, "Location"] <- sapply(crime_data[, "Location"], as.character)

lat_func <- function(location) {return(as.numeric(str_sub(strsplit(location, split = ",")[[1]], 2, -1)[1]))}
long_func <- function(location) {return(as.numeric(str_sub(strsplit(location, split = ",")[[1]], 1, -2)[2]))}


crime_data$longitude <- sapply(crime_data$Location, long_func)
crime_data$lattitude <- sapply(crime_data$Location, lat_func)
```


## Export dataset

```{r}
write.csv(crime_data, "data/clean_data.csv")
```

```

