---
title: "demographic analyse"
author: "LiuXuyang"
date: "9/26/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This scripts aims at analysing the demographic variables that we have and produce a better view on the places,timing for crime

What has been done ?
1) analyse on the distribution of victim age 
2) hypothesis test on the mean age between male and female
3) average age of victims based on race and sex
4) top 10 premise of a crime scene
5) time of a crime
6) number of crimes in different areas

TO DO :
- some detailed plots
- more analyses





## import the cleaned data

```{r library, echo=FALSE, warning=FALSE}
library(dplyr)
library(ggmap)
library(ggplot2)
library(dplyr)
library(lubridate)
library(tidyr)
library(stringr)
library(scales)
```

```{r}
crime_data<-read.csv("data/clean_data.csv")

```
## analyse on the age and sex variable
```{r}
mean(crime_data$Victim.Age,na.rm=TRUE)
sd(crime_data$Victim.Age,na.rm=TRUE)
summary(crime_data$Victim.Age,na.rm=TRUE)

female_age<-crime_data$Victim.Age[crime_data$Victim.Sex=="F"]
male_age<-crime_data$Victim.Age[crime_data$Victim.Sex=="M"]
summary(female_age,na.rm=TRUE)
summary(male_age,na.rm=TRUE)

ggplot(crime_data,aes(x=Victim.Age, fill = Victim.Sex, na.rm=TRUE)) + geom_bar()

```

# hypothesis test on the mean age between male and female
```{r}

t.test(female_age,male_age,alternative = "two.sided")  #mean age of victim is significantly smaller for female

```

the p-value is lower than 1%. Hence, we cannot accept the hypothesis that these means are equal.


## analyse on the average age of victims based on race and sex:
we can see that Hispanic has the largest number of victims and the average age is smallest

```{r}
crime_data%>%
  group_by(Victim.Descent.Global,Victim.Sex)%>%
  filter(!is.na(Victim.Age),!Victim.Descent.Global=="-",!Victim.Descent.Global=="",
         Victim.Sex=="F"|Victim.Sex=="M")%>%
  summarise(avg_age=mean(Victim.Age),count=n())%>%
  arrange(avg_age)
```
## time of a crime
```{r}
time_crime_data <- crime_data %>% filter(Year.Occurred == 2016, Month.Occurred == 10)

time_crime_data
time_func <- function(timestamp) {
  timestamp <- as.character(timestamp)
  while(nchar(timestamp) < 4) {
    timestamp <- paste("0", timestamp, sep = '')
    } 
  return(timestamp)
}

time_crime_data$Time.Occurred <- sapply(time_crime_data$Time.Occurred, time_func)
time_crime_data$Time.Occurred <- as.POSIXct(as.character(time_crime_data$Time.Occurred), format="%H%M", origin = "2000-01-01")


ggplot(time_crime_data,aes(x=Time.Occurred)) + geom_density() + scale_x_datetime(breaks = date_breaks("2 hour"), labels=date_format("%H:%M"), name = "Time of the day")

```

## top 10 premise of a crime scene
```{r}
crime_data%>%
  group_by(Premise.Description)%>%
  summarise(count=n())%>%
  arrange(desc(count))%>%
  head(10)

```


## number of crimes in different areas
for example:77th Street is the most dangerous area for female while Hollenbeck is comparatively a safe area.
```{r}
crime_data%>%
  group_by(Area.Name,Victim.Sex)%>%
  filter(!is.na(Victim.Age),Victim.Sex=="F"|Victim.Sex=="M")%>%
  summarise(avg_age=mean(Victim.Age),count=n())%>%
  arrange(desc(count),avg_age)

```
