---
title: "demographic analyse"
author: "LiuXuyang"
date: "9/26/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This scripts aims at analysing the demographic variables that we have and produce a better view on the places,timing for crime

What has been done ?
1) analyse on the distribution of victim age 
2) hypothesis test on the mean age between male and female
3) proportion of female/male victims among all victims of the same age
4) distribution of victim age between sex among different race
5) analyse on the average age of victims based on race and sex:
6) time of a crime
7) top 10 premise of a crime scene
8) number of crimes in different areas
9) some detailed plots

TO DO :

- feel free to add more analyses if you have any ideas





## import the cleaned data

```{r library, echo=FALSE, warning=FALSE}
library(dplyr)
library(ggmap)
library(ggplot2)
library(dplyr)
library(lubridate)
library(tidyr)
library(stringr)
library(scales)

```

```{r}
crime_data<-read.csv("data/clean_data.csv")

```
## analyse on the age and sex variable
```{r}
mean(crime_data$Victim.Age,na.rm=TRUE)
sd(crime_data$Victim.Age,na.rm=TRUE)
summary(crime_data$Victim.Age,na.rm=TRUE)

female_age<-crime_data$Victim.Age[crime_data$Victim.Sex=="F"]
male_age<-crime_data$Victim.Age[crime_data$Victim.Sex=="M"]
summary(female_age,na.rm=TRUE)
summary(male_age,na.rm=TRUE)

crime_data%>%
  filter(Victim.Sex=="F"|Victim.Sex=="M")%>%
  ggplot(aes(x=Victim.Age,fill=Victim.Sex,  na.rm=TRUE)) + geom_bar()+facet_wrap(~Victim.Sex)

```

# hypothesis test on the mean age between male and female
the p-value is lower than 1%. Hence, we cannot accept the hypothesis that these means are equal.
```{r}

t.test(female_age,male_age,alternative = "two.sided")  #mean age of victim is significantly smaller for female

```


## proportion of female/male victims among all victims of the same age
```{r}
age<-crime_data%>%select(Victim.Age,Victim.Sex)%>%filter(Victim.Sex=="F"|Victim.Sex=="M")

age<-age%>%group_by(Victim.Age,Victim.Sex)%>%summarise(count=length(Victim.Sex))%>%ungroup()%>%group_by(Victim.Age) %>% mutate(prop = count / sum(count)*100)
female<-filter(age,Victim.Sex=="F")
male<-filter(age,Victim.Sex=="M")
ggplot(female,aes(x=Victim.Age,y=prop)) + geom_line() + labs(x="Victime Age",y="propotion of female victims")
ggplot(male,aes(x=Victim.Age,y=prop)) + geom_line() + labs(x="Victime Age",y="propotion of male victims")

```




## distribution of victim age between sex among different race

```{r}

demographic <- crime_data %>% select(Victim.Age, Victim.Descent.Global, Victim.Sex) %>% 
 filter( !is.na(Victim.Age),!Victim.Descent.Global=="-",!Victim.Descent.Global=="",
         Victim.Sex=="F"|Victim.Sex=="M")%>%
  group_by(Victim.Age, Victim.Descent.Global, Victim.Sex) %>% 
  summarise(count = n())
Asian <- filter(demographic,  Victim.Descent.Global== "Asian")
Hispanic <- filter(demographic,  Victim.Descent.Global== "Hispanic")
Black<-filter(demographic,  Victim.Descent.Global== "Black")
White<-filter(demographic,  Victim.Descent.Global== "White")
Pacific_Islander <- filter(demographic,  Victim.Descent.Global== "Pacific Islander
")
Others<-filter(demographic,  Victim.Descent.Global=="Others")

ggplot(asian, aes(x = Victim.Sex, y = count, fill = as.factor(Victim.Age))) + 
  geom_bar(stat = 'identity', position = 'dodge')
ggplot(Hispanic, aes(x = Victim.Sex, y = count, fill = as.factor(Victim.Age))) + 
  geom_bar(stat = 'identity', position = 'dodge')
ggplot(Hispanic, aes(x = Victim.Age, y = count, fill = as.factor(Victim.Sex))) + 
  geom_bar(stat = 'identity', position = 'dodge')    #Obvious difference between male and female especially for ages around 25(young female)

```

## analyse on the average age of victims based on race and sex:
we can see that Hispanic has the largest number of victims and the average age is smallest
```{r}
avg_age<-crime_data%>%
  group_by(Victim.Descent.Global,Victim.Sex)%>%
  filter(!is.na(Victim.Age),!Victim.Descent.Global=="-",!Victim.Descent.Global=="",
         Victim.Sex=="F"|Victim.Sex=="M")%>%
  summarise(avg_age=mean(Victim.Age),count=n())%>%
  arrange(avg_age)
ggplot(avg_age,aes(x=Victim.Descent.Global,y=avg_age,fill=Victim.Sex))+geom_bar(stat = 'identity', position = 'dodge')+labs(x="race of victim",y="average age of victim")
       
```
## time of a crime
```{r}
time_crime_data <- crime_data %>% filter(Year.Occurred == 2016, Month.Occurred == 10)

time_crime_data
time_func <- function(timestamp) {
  timestamp <- as.character(timestamp)
  while(nchar(timestamp) < 4) {
    timestamp <- paste("0", timestamp, sep = '')
    } 
  return(timestamp)
}

time_crime_data$Time.Occurred <- sapply(time_crime_data$Time.Occurred, time_func)
time_crime_data$Time.Occurred <- as.POSIXct(as.character(time_crime_data$Time.Occurred), format="%H%M", origin = "2000-01-01")


ggplot(time_crime_data,aes(x=Time.Occurred)) + geom_density() + scale_x_datetime(breaks = date_breaks("2 hour"), labels=date_format("%H:%M"), name = "Time of the day")

```

## top 10 premise of a crime scene
```{r}
place<-crime_data%>%select(Premise.Description,Victim.Sex,Victim.Age)%>%
  filter(!is.na(Victim.Age), Victim.Sex=="F"|Victim.Sex=="M")%>%
  group_by(Premise.Description,Victim.Sex)%>%
summarise(count=n())%>%
  arrange(desc(count))%>%
head(10)
ggplot(place, aes(x =Premise.Description , y= count,fill=Victim.Sex)) + geom_bar(position = position_dodge(),stat = 'identity')  +
  theme(axis.text = element_text(angle= 45, hjust = 1))+labs(x="crime premises",y="number of victims")
  

```


## number of crimes in different areas
for example:77th Street is the most dangerous area for female while Hollenbeck is comparatively a safe area.
```{r}
area<-crime_data%>%
  select(Area.Name,Victim.Sex,Victim.Age)%>%
  filter(!is.na(Victim.Age), Victim.Sex=="F"|Victim.Sex=="M")%>%
  group_by(Area.Name,Victim.Sex)%>%
summarise(count=n(),avg_age=mean(Victim.Age))%>%
  arrange(desc(count))

ggplot(area,aes(x =Area.Name , y= count,fill=Victim.Sex)) + geom_bar(position = position_dodge(),stat = 'identity')  +
  theme(axis.text = element_text(angle= 45, hjust = 1))+labs(x="crime area",y="number of victims")
  

```
