---
title: "Final Report"
author: "Group B"
date: "September 29, 2017"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
    fig_width: 7
    fig_height: 6
    fig_caption: true
    df_print: tibble
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width = 10, fig.height = 7, fig.align = "center") 
```

```{r, include=FALSE}
crime_data<-read.csv("data/clean_data.csv")
```

\newpage

Introduction
=====================

Context
---------------------
Los Angeles (L.A) is one of the most vibrant cities in the United States with a high level of economic activity. It is the 2nd most populous city in the US after New York city and is home to a wide range of business and professional interests. Criminal activity in L.A is often heavily scrutinised given its diverse population and importance as a cultural hub. 

L.A is considered as one of the most dangerous cities in the US, with a high crime rate of 6.45 incidents per 1000 residents compared to the national median of 3.8 in 2015. According to Los Angeles Police Department (LAPD), crime rate in the city has fallen for 10 consecutive years from 2002 to 2012. However, in 2015, it was reported that for the first time in more than a decade, all categories of crime rose across the city (violent crime rose 20.2% and all crime was up 12.6% compared with 2014). The upward trend continued in 2016, with higher crime across four categories compared to 2015. 

Officials have attributed the increase to a variety of factors, including increased gang activity and a rise in the number of homeless people. With a high chance of roughly 1 in 33 to become a victim of either violent or property crime in L.A, it is important to focus efforts on crime prevention and education.

In order to learn more about patterns of crime in L.A and to come up useful suggestions to aid efforts in crime prevention, this paper looks into three main questions of crime patterns in L.A; firstly, who is more likely to be a victim; secondly, where are the accident-prone areas in L.A and thirdly, when are crimes more likely to occur. The dataset used in this paper contains information of crime occurred in L.A since 2010, with weekly update by City of Los Angeles. 


Theory
--------------------
Studies of criminal patterns and activities have in the past belonged to the domain of psychology and sociology. However, with the rise of criminal activities and increased sophistication of criminal operations, there is a need for more targeted crime prevention efforts. In the past decades there have been increased efforts in data collection of criminal activites which have allowed for quantitative analysis to better predict incidence of crime, likely victims of crime and a myriad of other questions. This paper aims to adopt statistical tools and visualisation efforts to paint a clearer picture of criminal activities in L.A and provide some useful insights and policy recommendations based on the analysis done. Our analysis will also be useful for crime prevention efforts from the victims' point of view, as we aim to highlight demographic and location factors that will make one more susceptible to crime. 

Data Description
=====================

The dataset contains information on crime incidents in Los Angeles. The source description (LAPD) states that the dataset may have some inaccuracies due to information being transferred from original crime statements that are typed on paper. As crime data contains sensitive personal information, fields that contain address information are only provided to the nearest hundred block. The dataset includes crime data from 2010 through September 2017.

Two separate csv files are provided with  Crime_Data_2010_2017  containing the main data and MO_Codes containing the description of MO codes that are included in the crime data for classification. 
The dataset is made up of 1.584.316 observations and 26 variables. To structure the variables, we split them into four groups: demographic, geographic, crime and time type variables. Demographic category consists of the victims age, sex and descent. The type of variables and a detailed description can be found in the table below: 

_Demographics_

| Variable      |    Type     |   Description      |
| ------------- | ----------- | :---------------------------------------------------      |
| Victim.Age    |     dbl     |      Two character numeric   |
| Victim.Sex    |    fctr     |     F - Female M - Male X - Unknown  |
|Victim.Descent |    fctr     |      Descent Code: A - Other Asian B - Black C - Chinese D - Cambodian F - Filipino G - Guamanian H - Hispanic/Latin/Mexican I - American Indian/Alaskan Native J - Japanese K - Korean L - Laotian O - Other P - Pacific Islander S - Samoan U - Hawaiian V - Vietnamese W - White X - Unknown Z - Asian Indian    |



The geographical category contains variables relating to the geographical occurrence of crime and reporting of crimes. Variables include the area ID, the name of the area, the district reporting the crime, the premise code, a premise description, the address, the cross street of rounded address and the location where the crime occurred. The type of variables and a detailed description can be found in the table below: 

_Geographic_

| Variable            |    Type     |   Description      |
| -------------       | ------------- | :-------------------------------------------------      |
| Area.ID             |  int    |  The LAPD has 21 Community Police Stations referred to as Geographic Areas within the department. These Geographic Areas are sequentially numbered from 1-21. |
| Area.Name           |  fctr    |   The 21 Geographic Areas or Patrol Divisions are also given a name designation that references a landmark or the surrounding community that it is responsible for. For example 77th Street Division is located at the intersection of South Broadway and 77th Street, serving neighborhoods in South Los Angeles.   |
| Reporting.District  |   int   |  A four-digit code that represents a sub-area within a Geographic Area. All crime records reference the "RD" that it occurred in for statistical comparisons.    |
| Premise.Code        | dbl     |  The type of structure, vehicle, or location where the crime took place.    |
| Premise.Description | fctr     |  Defines the Premise Code provided    |
| Address             |   fctr   |  Street address of crime incident rounded to the nearest hundred block to maintain anonymity.    |
| Cross.Street  |  fctr   | Cross Street of rounded Address.  |
| Location      |   fctr   |   The location where the crime incident occurred. Actual address is omitted for confidentiality. XY coordinates reflect the nearest 100 block.   |
             

The crime category contains all variables that describe the incidents of crime in more detail such as the type of crime, the weapons used or the current status of the crime. The variables we assorted to this category include the number of the crime on record, the weapons used and their description, the status of the crime (code and description), then crime codes and their description as well as the modus operandi associated with the suspect in commission of the crime.

_Crime_

| Variable       |    Type     |   Description      |
| ------------- | -------------   | :------------------------------------------------------------------------      |
|  DR.Number        |      int   |    Division of Records Number: Official file number made up of a 2 digit year, area ID, and 5 digits       |
|  Weapon.Used.Code |     dbl    |   The type of weapon used in the crime.        |
|  Weapon.Description|  fctr     |    Defines the Weapon Used Code provided.       |
|  Status.Code      |   fctr     |    Status of the case. (IC is the default)       |
|  Status.Description|    fctr   |   Defines the Status Code provided.        |
|  Crime.Code.1     |    fctr    |    Indicates the crime committed. Crime Code 1 is the primary and most serious one. Crime Code 2, 3, and 4 are respectively less serious offenses. Lower crime class numbers are more serious.      |
|  Crime.Code.2     |    fctr    |  May contain a code for an additional crime, less serious than Crime Code 1.      |
|  Crime.Code.3     |    fctr    |    May contain a code for an additional crime, less serious than Crime Code 1.       |
|  Crime.Code.4     |    fctr    | May contain a code for an additional crime, less serious than Crime Code 1.          |
|  Crime.Code       |    int     |     Indicates the crime committed. (Same as Crime Code 1)      |
|  Crime.Code.Description|  fctr |   Defines the Crime Code provided.        |
|  MO.Codes         |   fctr     |     Modus Operandi: Activities associated with the suspect in commission of the crime.       |



The final category groups all variables related to time. It contains a variable that contains the reported date, the date and time occurrence.

_Time_

| Variable      |    Type         |   Description  |
| ------------- | -------------   | :------------------------     |
| Date.Reported |     fctr     |   MM/DD/YYYY   |
| Date.Occurred |    fctr    |   MM/DD/YYYY   |
| Time.Occurred |      int     |    In 24 hour military time.   |

Strengths and Weaknesses of Dataset
-------------------

### Strengths:

1. Large number of observations 

The dataset is comprehensive and documents criminal activities in L.A. from 2010 to September 2017. The large number of observations means that our analysis will be more robust and enable us to more accurately make predictions on future criminal activties. 

2. Many variables regarding each criminal offence were collected and documented  

We can conduct analysis on different areas with respect to crime in L.A with the data that we have. The data collected was extensive and detailed, with information on demographics, type of crime, and timings amongst other things. This will again allow us to study and identify interesting patterns with regards to criminal activities in L.A. 

### Weaknesses:
1. Lack of socio-economic information

While the dataset was comprehensive, it did not contain information on the socio-economic status of victims or perpetrators of crimes. Having such information would allow us to make more interesting inferences on likely victims of crime and also the type of crime committed. It is highly likely that socio-economic information will be as powerful as demographics, if not more powerful, in predicting criminal activities. 

2. Lack of proper classification for different types of crime

The classification of types of crime in the dataset was messy and was not conducive for analysis, making it difficult to study the correlation between types of crime being committed and other variables such as area and demographics. This is because the crime description in the original dataset differs even for crimes that are broadly similar in nature. We thus have to go through the dataset and make classifications that are logical and at the same time, conducive for analysis. 

Data Cleaning Description
-------------------
As the data is provided in two different csv files. The first step that we took was to merge the crime_data and code_data into one single dataset. Then we looked at the date columns (date occured and date reported) and reformated each date to three new columns. Thus creating a new colum for the day occured, month occured and year occured as well as day reported, month reported and year reported. 
For the completeness of full information on every year, we have omitted data from the year 2017 and will focus on the data from 2010 to 2016 included. 

In order to make an interesting analysis we wanted to work with the information on victim descent. The abbreviations for victim descent in the original dataset, however, made analysis a little impractical as they weren't intuitively understandable (e.g. "D" standing for "Cambodian"). This is why we labeled the descent variables with the full description. (e.g. "W" being "White" and "D" being "Cambodian").


As there were some very specific subcategories for America (such as Alaskan Native)  we also added an additional more global column on victim descent to be able to work with both the more detailed descent information and the more global descent variables. We reduced the global descent column to contain six groups:


_Victim Descent_

| Victim Descent Global Variables |
| ------------- |
| White |
| Black |
| Hispanic |
| Other | 
| Asian |
| Pacific |

In order to simplify the mapping of location information, we also extracted longitude and latitude from the location column and created additional, separate columns for longitude and latitude. 

The data also covers and categorizes different types of crime in extensive detail. In order to extract valuable insights, we simplified the crime type variables by grouping them into more general categories. This reduced the 135 variables to sixteen more general variables. 

As we put the focus of our analysis on understanding Los Angeles' victim profiles we decided not to use the data that is provided on crime suspects. 






Demographic
=====================

_Firstly,we want to find out what kind of people are more likely to be a victim of crime and thus look at some demographic variables such as age,sex and ethnicity._

Age and sex distribution
-------------------

```{r library, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr) 
library(ggmap)
library(ggplot2)
library(dplyr)
library(lubridate)
library(tidyr)
library(stringr)
library(scales)

```

Here we begin with a summary of the age among all victims.The summary of the victim age shows the youngest victim is only 10 years old and the oldest being 99 years old. The mean age of victim is around 36 years old. 
```{r , echo=FALSE}

##distribution of age among all victims
summary(crime_data$Victim.Age,na.rm=TRUE)
```

Typically the age pattern of victims between male and female are not the same.We then construct a summary for male and female respectively and a histogram plot to see if it is the case.

```{r}
#summary of female age and male age respectively
female_age<-crime_data$Victim.Age[crime_data$Victim.Sex=="F"]
male_age<-crime_data$Victim.Age[crime_data$Victim.Sex=="M"]
summary(female_age,na.rm=TRUE)
summary(male_age,na.rm=TRUE)
#plot
crime_data%>%filter(Victim.Sex=="F"|Victim.Sex=="M")%>%
ggplot(aes(x=Victim.Age,fill=Victim.Sex)) + geom_histogram(binwidth = 1,position="dodge")+labs(x="Victim Age",y="Number of Victims")

```

The minimum and maximum of victim age are the same for both sex. However,the female victim age is smaller(37.52 years old) on average than for male(38.72 years old).
From the overlapping pattern of the histogram plot above, it is obvious that male are more likely to be a victim of crime at a young age(10-15 years old) or from 40 to 70 years old while female tend to be more in danger between around 15 to 35 years old, especially aged between 18 and 25. For example, at age 25,number of female victims are approximately 7500 higher than male victims.


_Hypothesis testing_

As we have seen a different pattern in the victim age for male and female above, we want to use student t-test to check if the difference exists statistcally or is due to random variation. 

```{r , echo=FALSE}
# Code here
t.test(female_age,male_age,alternative = "two.sided")

```

A t-test is conducted build on the null hypothesis that there is no significant difference in the mean victim age between male and female.Based on the t-test,a p-value of less than 2.2e-16 is really low and we can conclude that there is strong evidence in rejecting the null hypothesis that the difference in means is 0.Thus,mean age of victim is significantly smaller for female.


Ethnicity
-------------------

Now that we have some clue about the relationship between age and gender,we want to dig more by adding another ethnicity variable.Below is a boxplot of victim age of male and female based on different ethnicity.

```{r , echo=FALSE}
#average age of victims based on ethnicity and gender(Hispanic has the lowerst avg age)
avg_age<-crime_data%>%
  group_by(Victim.Descent.Global,Victim.Sex)%>%
  filter(!is.na(Victim.Age),!Victim.Descent.Global=="-",!Victim.Descent.Global=="",
         Victim.Sex=="F"|Victim.Sex=="M")%>%
  summarise(avg_age=mean(Victim.Age),count=n())%>%
  arrange(avg_age)

#option1:barchart of mean age between different Ethnicity
#ggplot(avg_age,aes(x=Victim.Descent.Global,y=avg_age,fill=Victim.Sex))+geom_bar(stat = 'identity', position = 'dodge')+labs(x="race of victim",y="average age of victim")

#option2:boxplot of age between different Ethnicity(chosen)
crime_data%>%
  filter(Victim.Sex=="F"|Victim.Sex=="M",!Victim.Descent.Global=="-",!Victim.Descent.Global=="")%>%
  ggplot(aes(x=Victim.Sex,y=Victim.Age,fill=Victim.Descent.Global))+geom_boxplot()+labs(x="Gender",y="Victim Age")
```
From the boxplot based on ethnicity and gender,Hispanic have the lowest median age among all ethnicity groups and female Hispanic is the lowest(around 33 years old).For Blacks and Hispanic,female victim tends to be younger while it is not that obvious for other ethinicty groups.

We also have a histogram plot of victims counts with different gender and ethnicity below.

```{r}
#number of vitims with different gender and ethnicity
crime_data%>%
  filter(Victim.Sex=="F"|Victim.Sex=="M",!Victim.Descent.Global=="-",!Victim.Descent.Global=="")%>%
  ggplot(aes(x=Victim.Age,fill=Victim.Sex,  na.rm=TRUE)) + geom_bar(position="dodge")+facet_wrap(~Victim.Descent.Global)+
  labs(x="Victime Age",y="Number of victims")
```
From the above plot,it is obvious that Hispanic account for the largest part of victims,followed by black and white victims. Also,there are observable difference in the age distribution between male and female for the three ethnicity group.Focus on hispanic victims,female aged below around 40 are much more likely to be a victim than male.
```{r}
#Thus focus on Hispanic
#demographic <- crime_data %>% select(Victim.Age, Victim.Descent.Global, Victim.Sex) %>% 
# filter( !is.na(Victim.Age),!Victim.Descent.Global=="-",!Victim.Descent.Global=="",
#         Victim.Sex=="F"|Victim.Sex=="M")%>%
#  group_by(Victim.Age, Victim.Descent.Global, Victim.Sex) %>% 
#  summarise(count = n())

#Hispanic <- filter(demographic,  Victim.Descent.Global== "Hispanic")

#ggplot(Hispanic, aes(x = Victim.Age, y = count, fill = as.factor(Victim.Sex))) + 
#  geom_bar(stat = 'identity', position = 'dodge')    
```


_Hypothesis testing_
We want to carry out hypothesis testing to determine whether it is indeed the case according to the plot.
```{r}
Hispanic_female1<-crime_data%>%filter(Victim.Descent.Global=="Hispanic")
Hispanic_female<-Hispanic_female1$Victim.Age[Hispanic_female1$Victim.Sex=="F"]
Hispanic_male1<-crime_data%>%filter(Victim.Descent.Global=="Hispanic")
Hispanic_male<-Hispanic_male1$Victim.Age[Hispanic_male1$Victim.Sex=="M"]
t.test(Hispanic_female,Hispanic_male,alternative = "two.sided")

black_female1<-crime_data%>%filter(Victim.Descent.Global=="Black")
black_female<-black_female1$Victim.Age[black_female1$Victim.Sex=="F"]
black_male1<-crime_data%>%filter(Victim.Descent.Global=="Black")
black_male<-black_male1$Victim.Age[black_male1$Victim.Sex=="M"]
t.test(black_female,black_male,alternative = "two.sided")

white_female1<-crime_data%>%filter(Victim.Descent.Global=="White")
white_female<-white_female1$Victim.Age[white_female1$Victim.Sex=="F"]
white_male1<-crime_data%>%filter(Victim.Descent.Global=="White")
white_male<-white_male1$Victim.Age[white_male1$Victim.Sex=="M"]
t.test(white_female,white_male,alternative = "two.sided")


```
In the t-tests above,all three p-values are smaller than 0.05 which means that the difference in mean age is significant for all three ethnicity groups.Female Hispanic victims are around 6 years younger on average than male Hispanic victims.For black people,female victims are around 3 years younger on average than male victims.However,as for white people,the average age is approximately the same(with a difference of between 0.02 to 0.25).

Also,we want to know if the proportion of crime victims based on different ethnicity are the same as in the real population.Therefore,we calculate the proportion of white,black,hispanic victims below.
```{r , echo=FALSE}
crime_data1<-filter(crime_data,!crime_data$Victim.Descent=="")
sum(crime_data1$Victim.Descent.Global=="White")/nrow(crime_data1)
sum(crime_data1$Victim.Descent.Global=="Black")/nrow(crime_data1)
sum(crime_data1$Victim.Descent.Global=="Hispanic")/nrow(crime_data1)

```
According to the population of LA, non-Hispanic white people was 28.7% while black people was 9.6% of the population. While in the crime data,white people was 27.4% and black people was 17.8%.Thus,there are huge difference between the population proportion with the crime proportion for black people.



We can see that the variables we discussed above are correlated with each other from the plots,now we construct a chi-squared test to verify the dependence shown in the plots.
```{r}
chisq.test(crime_data$Victim.Descent,crime_data$Victim.Age)
chisq.test(crime_data$Victim.Descent,crime_data$Victim.Sex)
chisq.test(crime_data$Victim.Age,crime_data$Victim.Sex)

```
From the chi-squared tests above,it is obvious that there are certain degree of dependence between age and sex,age and ethnicity,sex and ethnicity.

_summary_

From the demographic analysis carried out so far,we found that people with certain demographic characteristics are more likely to be a victim of crime. For example,Hispanic young female aged aroung 25 years old are more likely to become crime victim.




relationship with type of crime
-------------------
As we now have some understanding on the victim information,we want to find out whether the characteristics of victims  differs in different types of crime.
```{r , echo=FALSE}
#type of crime with gender
type<-crime_data%>%select(crime_type,Victim.Sex,Victim.Age)%>%
  filter(!is.na(Victim.Age), Victim.Sex=="F"|Victim.Sex=="M")%>%
  group_by(crime_type,Victim.Sex)%>%
summarise(count=n())%>%
  arrange(desc(count))
ggplot(type, aes(x =crime_type , y= count,fill=Victim.Sex)) + geom_bar(position = position_dodge(),stat = 'identity')  +
  theme(axis.text = element_text(angle= 45, hjust = 1))+labs(x="crime type",y="number of victims")+scale_y_continuous(breaks=c(10000,20000,40000,80000,100000,200000,300000))
```
From the barplot on crime type above,burglary,battery,assault and vandalism are the most likely crime types.Burglary and assault tends to be aiming more on male while battery and other sexual offences have more female victims.

```{r}
#boxplot of victim age between different type of crimes and gender
#crime_data%>%
#  filter(Victim.Sex=="F"|Victim.Sex=="M",!Victim.Descent.Global=="-",!Victim.Descent.Global=="")%>%
#  group_by(crime_type,Victim.Sex)%>%
  
#  ggplot(aes(x=Victim.Sex,y=Victim.Age,fill=crime_type))+geom_boxplot()

```
We are also intersted in the pattern of crime type with different ethnicity.Overall,burglary/theft occurs most frequently for all ethnicity groups.The burglary/theft proportion is the lowest for black victims.As for the proportion of assault and battery,asians,white,asian,pacific islanders share similar proportion pattern whereas black and hispanic people have higher proportion in this two crime types.
```{r}
crime_data %>% filter(!Victim.Descent.Global=="-",!Victim.Descent.Global==" ") %>% ggplot(aes(x=Victim.Descent.Global, fill=crime_type))+ geom_bar(position='fill') + labs(x="Victim's Ethnicity", y= "Proportion of Crimes")
```





Area distribution
=====================

We have seen who are the victims of the crime, now let's focus on the location of these crimes. Of course, we can make the hypothesis that the location depends on the type of crime and on the victim.

number of crimes in different areas
-------------------

First, we want to study the distribution of crime in the different areas.

```{r , echo=FALSE}
top5_crime <-  crime_data %>% select(Area.Name, crime_type) %>% group_by(crime_type, Area.Name) %>% summarise(count = n()) %>% top_n(5, wt =  count) 
top5_crime

ggplot(crime_data, aes(x = crime_type)) + geom_bar() + facet_wrap(~ Area.Name) + theme(axis.text = element_text(angle= 60, hjust = 1))
```

From these graphs, we can see that the distribution of the type of crime is slightly similar in the different areas. 

_Hypothesis testing_

Let's conduct a X-squared test to test the hypothesis whether the crime area is independent of the type of a crime at .05 significance level.

```{r}
tbl = table(crime_data$Area.Name, crime_data$crime_type) 
chisq.test(tbl)
```

As the p-value is lower than the .05 significance level, we reject the null hypothesis that the crime area is independent of the type of a crime.

Another way to address the problem is to look at the crime density for different type of crime in Los Angeles.


Area distrubution per type of crime 
-------------------

```{r, fig.width=7, fig.height=10}

crime_data_coord <- crime_data %>% select(longitude, lattitude, Year.Occurred, crime_type) %>% filter(Year.Occurred == 2016)


LAMap <- ggmap(
  get_map("Los Angeles", zoom = 11), extent = "device", 
  legend = "topright")

LAMap +
  stat_density2d(aes(x = longitude, y = lattitude, fill = ..level..),
    size = 2, bins = 4, data = crime_data_coord, geom = "polygon", na.rm = TRUE) +
  scale_fill_gradient("Crime\nDensity") +
  scale_alpha(range = c(.4, .8), guide = FALSE) +
  guides(fill = guide_colorbar(barwidth = 1, barheight = 6)) + facet_wrap( ~ crime_type)
```

We can see from the plot above the different area densities for each type of crime. As we will expect, for each type of crime, the region with the highest density of crime is close to central L.A.. There are a few main observations that we can make based on the plot. 

Firstly, we observe that homicides, gun shot crimes and kidnapping have fairly similar area distributions, with the highest density located around the area south of downtown Los Angeles.

Secondly, we can see that rape crimes, burglary, robbery, vandalism and other sexual offences are most concentrated in downtown Los Angeles.

Lastly, we observe that crimes like arson and contempt of court have a large area distribution. 




Time
=====================

_Text here_

Day Time according to type of crime
-------------------

(ex : fraud in the day, rape a night, burglary during the day etc...)

```{r , echo=FALSE}
# Code here
```

_Text here_

_Hypothesis testing_

```{r , echo=FALSE}
# Code here
```

Day Time according to sex
-------------------

```{r , echo=FALSE}
# Code here
```

_Text here_

_Hypothesis testing_

```{r , echo=FALSE}
# Code here
```

Correlation between time reported - time occured and type of crime
-------------------

```{r , echo=FALSE}
# Code here
```

_Text here_

_Hypothesis testing_

```{r , echo=FALSE}
# Code here
```

Correlation between time reported - time occured and case solved or not for a specific month
-------------------

```{r , echo=FALSE}
# Code here
```

_Text here_

_Hypothesis testing_

```{r , echo=FALSE}
# Code here
```


Public holidays impact
-------------------
```{r, eval=FALSE}

#Exploratory plot
ggplot(crime_data,aes(x=Date.Occurred.C,color=public_holiday))+geom_bar()+scale_color_manual(values=c("red","blue"))

crime_data%>%
  group_by(public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(public_holiday) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(desc(average.crime.per.day))


crime_data%>%
  filter(Day.Occurred=="01" & Month.Occurred=="01") %>%
  group_by(Date.Occurred.C) %>%
  summarise(count=n())
    
crime_data%>%
  group_by(Jan1=ifelse(Day.Occurred=="01" & Month.Occurred=="01","1st Jan","Other Days"))%>%
  summarise(Average.Report.Time=mean(Time.Between.Occured.Reported)) %>%
  arrange(desc(Average.Report.Time))


crime_data%>%
  filter(Day.Occurred!="01" & Month.Occurred!="01")%>%
  summarise(Occured.Reported.Gap.SD=sd(Time.Between.Occured.Reported))

```

Police always releases crime prevention tips before holidays, which gives us an impression that the number of crime occured on a holiday is generally higher than that on a regular day. We are interested in knowing whether our dataset support this impression to be true or not.

```{r}

crime_data%>%
  group_by(public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(public_holiday) %>%
  summarise(Average.Crime.per.Day=round(mean(count),1)) %>%
  arrange(desc(public_holiday))

```
To begin with, we have extract a list of holiday dates (not including Sundays) in LA from 2010 - 2016 from the Internet to catagorise crime occured dates to holiday and non-holiday. The avereage number of crime per day is on public holidays is 577.5 and that on non-public holidays is 559.8, which is a good start as it looks align with the impression.

```{r}
    
Jan1df1 <- crime_data%>%
  group_by(Jan1=ifelse(Day.Occurred=="01" & Month.Occurred=="01","1st Jan","Other Days"),Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(Jan1) %>%
  summarise(Average.Crime.per.Day=round(mean(count),1))

Jan1df2 <- crime_data%>%
  group_by(Jan1=ifelse(Day.Occurred=="01" & Month.Occurred=="01","1st Jan","Other Days"))%>%
  summarise(Average.Report.Time=round(mean(Time.Between.Occured.Reported),1))

Jan1df3 <- crime_data%>%
  group_by(Jan1=ifelse(Day.Occurred=="01" & Month.Occurred=="01","1st Jan","Other Days"))%>%
  summarise(SD.Report.Time=round(sd(Time.Between.Occured.Reported),1))

merge.data.frame(merge.data.frame(Jan1df1,Jan1df2,by="Jan1"),Jan1df3,by="Jan1")

```

However, we also found a pattern when exploring the data; number of crime on 1st Janurary in each year is extremly high comparing to othere days, and as 1st Jan is usually a public holiday, this would distort the picture. Besides, there is also a significant difference in the average reporting time (number of day between when the crime ocurred and reported) and the standard deviation of the distribution of reporting time.

Unfortunately we could not find any information on the Internet or from the source of the dataset that could explain the peaks on 1st Janurary. The most logical reason of this could be some of the cases were occured in the year but on an unknown day, and instead of keeping the occured day NA or missing, it was set as the 1st day of the year.

In order to have a meaningful comparison between number of crime cases on holidays and regular days, we have to remove the cases that were not truly occured on 1st Jan. As there is no indicator in the dataset pointing out those cases, the best estimator we have is number of days between occured and reported. Assuming the crimes on 1st Janurary would have the same distribution as other dates in a year, we decided to exclude cases pccured on 1st Jan with time difference between occured and reported more than 14.4 + 2*88.7 = 192 days. In theory, this range should have covered over 95% of the cases on 1st Jan.

```{r}

crime_data$Jan1.exclude.192 <- crime_data$Day.Occurred=="01" & crime_data$Month.Occurred=="01" & crime_data$Time.Between.Occured.Reported>192


cJan1df1 <- crime_data%>%
  filter(Jan1.exclude.192==FALSE)%>%
  group_by(Jan1=ifelse(Day.Occurred=="01" & Month.Occurred=="01","1st Jan","Other Days"),Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(Jan1) %>%
  summarise(Average.Crime.per.Day=round(mean(count),1))

cJan1df2 <- crime_data%>%
  filter(Jan1.exclude.192==FALSE)%>%
  group_by(Jan1=ifelse(Day.Occurred=="01" & Month.Occurred=="01","1st Jan","Other Days"))%>%
  summarise(Average.Report.Time=round(mean(Time.Between.Occured.Reported),1))

cJan1df3 <- crime_data%>%
  filter(Jan1.exclude.192==FALSE)%>%
  group_by(Jan1=ifelse(Day.Occurred=="01" & Month.Occurred=="01","1st Jan","Other Days"))%>%
  summarise(SD.Report.Time=round(sd(Time.Between.Occured.Reported),1))

merge.data.frame(merge.data.frame(cJan1df1,cJan1df2,by="Jan1"),cJan1df3,by="Jan1")

```

The way we use to exclude cases on 1st Jan is definiely not prefer, the standard derivation of cases on 1st Jan is lower than that on other days as we have a sharp cut at 192 days. But it is the best way we have to reduce some of the 'noise' and have excluded half of the cases on 1st Jan.

```{r}

crime_data%>%
  filter(Jan1.exclude.192==FALSE)%>%
  group_by(public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(public_holiday) %>%
  summarise(Average.Crime.per.Day=round(mean(count),1)) %>%
  arrange(desc(public_holiday))

```

And the average number of crime per day on public holidats is now less than that of that on non-public holidays, after excluding some of the 1st Jan cases. Before moving on to the hypothesis testing on whether there is more or less crime cases on a public holidays, we still have one question, are the natural of Sundays the same as public holidays, which most of people are not required to work and shop closes early on the day, in terms of number of crime cases per day?


```{r}

crime_data$Sundays.PH.Regular <- ifelse(crime_data$public_holiday=="Public Holidays","Public Holidays",ifelse(crime_data$Sundays=="Sunday","non-PH Sundays","not PH or Sunday"))


PH_S_df1 <- crime_data%>%
  filter(Jan1.exclude.192==FALSE)%>%
  group_by(Sundays.PH.Regular,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(Sundays.PH.Regular) %>%
  summarise(Average.Crime.per.Day=round(mean(count),1))

PH_S_df2 <- crime_data%>%
  filter(Jan1.exclude.192==FALSE)%>%
  group_by(Sundays.PH.Regular)%>%
  summarise(Average.Report.Time=round(mean(Time.Between.Occured.Reported),1))

PH_S_df3 <- crime_data%>%
  filter(Jan1.exclude.192==FALSE)%>%
  group_by(Sundays.PH.Regular)%>%
  summarise(SD.Report.Time=round(sd(Time.Between.Occured.Reported),1))

merge.data.frame(merge.data.frame(PH_S_df1,PH_S_df2,by="Sundays.PH.Regular"),PH_S_df3,by="Sundays.PH.Regular") %>% arrange(Average.Crime.per.Day)

Sunday.count <- crime_data%>%
  filter(Jan1.exclude.192==FALSE & Sundays.PH.Regular=="non-PH Sundays")%>%
  group_by(Sundays.PH.Regular,Date.Occurred.C)%>%
  summarise(count=n())
PH.count <- crime_data%>%
  filter(Jan1.exclude.192==FALSE & Sundays.PH.Regular=="Public Holidays")%>%
  group_by(Sundays.PH.Regular,Date.Occurred.C)%>%
  summarise(count=n())

t.test(Sunday.count$count,PH.count$count,alternative="two.sided")

```

Not surprisingly, the mean number of crime cases per day on Public Holidays and on Sundays are not much different.
And the t-test also indicate that there is no difference between the mean number of crime cases in Sundays and Public Holidays.
Therefore, Sundays and Public Holidays could be grouped in testing whether there is a difference between number of crime cases in Holidays(Public Holidays and Sundays) and the other days.


```{r}
crime_data$Sundays.PH.Regular2 <- ifelse(crime_data$public_holiday=="Holidays","Public Holidays",ifelse(crime_data$Sundays=="Sunday","Holidays","not PH or Sunday"))


H_R_df1 <- crime_data%>%
  filter(Jan1.exclude.192==FALSE)%>%
  group_by(Sundays.PH.Regular2,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(Sundays.PH.Regular2) %>%
  summarise(Average.Crime.per.Day=round(mean(count),1))

H_R_df2 <- crime_data%>%
  filter(Jan1.exclude.192==FALSE)%>%
  group_by(Sundays.PH.Regular2)%>%
  summarise(Average.Report.Time=round(mean(Time.Between.Occured.Reported),1))

H_R_df3 <- crime_data%>%
  filter(Jan1.exclude.192==FALSE)%>%
  group_by(Sundays.PH.Regular2)%>%
  summarise(SD.Report.Time=round(sd(Time.Between.Occured.Reported),1))

merge.data.frame(merge.data.frame(H_R_df1,H_R_df2,by="Sundays.PH.Regular2"),H_R_df3,by="Sundays.PH.Regular2") %>% arrange(Average.Crime.per.Day)

Holiday.count <- crime_data%>%
  filter(Jan1.exclude.192==FALSE & Sundays.PH.Regular2=="Holidays")%>%
  group_by(Sundays.PH.Regular,Date.Occurred.C)%>%
  summarise(count=n())
Regular.count <- crime_data%>%
  filter(Jan1.exclude.192==FALSE & Sundays.PH.Regular2=="not PH or Sunday")%>%
  group_by(Sundays.PH.Regular,Date.Occurred.C)%>%
  summarise(count=n())

t.test(Holiday.count$count,Regular.count$count,alternative="less")


```

The average number of crime cases on Holidays (Public Holidays and Sundays combined) is less than that on regular days, shown by the t-test, in 99% confidence level, which is different from the general perception that there are more crime cases on holidays.


```{r}
#By crime type 
crime_data_excluded_1Jan_192 <- crime_data%>%
  filter(Jan1.exclude.192==FALSE) %>% 
  select(crime_type,Sundays.PH.Regular2,Date.Occurred.C) %>%
  group_by(crime_type,Sundays.PH.Regular2,Date.Occurred.C) %>% summarise (countperday=n()) %>% ungroup() %>% group_by(crime_type,Sundays.PH.Regular2) %>% summarise (average_per_day=mean(countperday))

crime_data_excluded_1Jan_192

PH_Crimetype_tbl <- xtabs(average_per_day~crime_type+Sundays.PH.Regular2,crime_data_excluded_1Jan_192)
PH_Crimetype_tbl
```

Most of crime type has less ocuuring rate on public holidays, but it likes look assault, battery, gunshots, rape and vandalism has a higher occuring rate in public holidays.


Prediction and logistic regression
=====================

_Data Cleaning_

```{r}
# Remove missing values for victim age and premise code
crime_data[, "Victim.Sex"] <- sapply(crime_data[, "Victim.Sex"], as.character)
crime_data_NA <- crime_data[!is.na(crime_data$Victim.Age) & !is.na(crime_data$Premise.Code) & (crime_data$Victim.Sex == "F" | crime_data$Victim.Sex == "M"),]
crime_data[, "Victim.Sex"] <- sapply(crime_data[, "Victim.Sex"], as.factor)

```

_Training set and learning set_

```{r}
train_data <- crime_data_NA[crime_data_NA$Year.Occurred != 2016, ]
test_data <- crime_data_NA[crime_data_NA$Year.Occurred == 2016, ]
```

_Predict the type of crime_

First, we try to predict the type of crime according to different parameters such as the age of the potential victim, the sex, the ethnicity and the area

```{r}
#Multinomial Logistic Regression

library("nnet")
library(pscl)

model <- multinom(Area.Name ~ Victim.Age + Victim.Sex + Victim.Descent +  crime_type, data = test_data)

summary <- summary(model)

pR2(model)

test_data_predict <- test_data %>% select(Victim.Age, Victim.Sex, crime_type)
predict_area <- predict(model, test_data_predict, type = 'class')

sum(test_data$Area.Name == predict_area)/length(predict_area)

```


Discussion
=====================

What results did you find?	
-------------------
We have studied the patterns of crime in L.A in three different aspects. From the demographic point of view, we have information about the characteristics of people that are most likely to be a victim:at a young age, females are more possible than male to be involved in a crime. Also, hispanic people has the highest proportion in the number of victims. Hispanic young woman around 25 years old are the most dangerous group in L.A according to the analysis into the data. In addition, Male vitims in crimes like burglary and assault are higher than female while female victims account for a larger part in battery and other sexual offences.Secondly, looking into the crime-prone areas in L.A,
we found that 

Why is this interesting?
-------------------
With the information extracted from the L.A crime dataset,it is possible to provide useful suggestions for LA police in order to reduce the number of either citizens or tourists of L.A from being hurt.In addition,we are interested in the general pattern of crime and curious about what will happen in the future.Thus,a prediction of the crime based on the recent dataset is crucial for the future crime prevention.
Help LA police, predict the crime, prevention for the potential victims

What would be the next steps?	
-------------------
In this paper, we focus on the victim of crime in order to help prevent certain crimes. The next step could be carrying out investigation in the suspect of crime to help police find suspects and solve crime more efficiently.  
crime type prediction
area crime prediction
suspect



