---
title: "Final Report"
author: "Group B"
date: "September 29, 2017"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
    fig_width: 7
    fig_height: 6
    fig_caption: true
    df_print: tibble
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width = 10, fig.height = 7, fig.align = "center") 
```

```{r, include=FALSE}
crime_data<-read.csv("data/clean_data.csv")
```

\newpage

Introduction
=====================

Context 
----------------

Los Angeles (L.A) is one of the most important city in the United States, with a diverse economy that ranges over a broad range of business and professional interests. It is also the 2nd largest city in the US, after New York City. The bustling nature of Los Angeles, coupled with its diverse population, means that crime is always a big issue in the city. L.A is home to 45,000 gang members and is also known as the "Gang Capital of America". 

With a considerably higher rate of violent crime at 6.45 incidents per 1000 residents compared to US national median of 3.8 per 1000 residents in 2015 (based on FBI crime data), L.A is amongst the most dangerous cities in US. According to Los Angeles Police Department (LAPD), the crime rate in city had declined for 10 consecutive years from 2002 to 2012. However, in 2015, LAPD reported that for the first time in more than a decade, all categories of crime rose across the city (violent crime rose 20.2% and all crime was up 12.6% compared with 2014). The upward trend continued in 2016, with higher crime across four categories compared to 2015. 

Officials have attributed the increase in crime rate to a number of factors, including increased gang activity and a rise in the number of  homeless people. With a high chance of 1 in 33 to become a victim of either violent or property crime in L.A, it is important to focus efforts on crime prevention and public safety. In order to learn more about patterns of crime in L.A and to provide some guidance on crime prevention, this paper tries to answer three main questions of crime in L.A. Firstly, who is more likely to be a victim; secondly, where is the accident-prone place in L.A and lastly, when the crime is most likely to occur. The dataset used in this paper contains information of crime occurred in L.A since 2010, with weekly update by City of Los Angeles. As this data is transcribed from original crime reports that are typed on paper and therefore there may be some inaccuracies within the data.

Theory
-------------------
Crime patterns have long been heavily studied and with the increase in better quality data, quantitative methods are increasingly being deployed to better understand crime patterns and to answer the questions that we have posed above. Prior to this, crime patterns were  studied heavily by disciplines such as sociology and psychology. However, the need for better policy design to curb increasing levels of crime means that economic tools are being adopted to analyse the marginal benefit and cost of various policy initiatives. This resulted in massive improvements in data quality and availability, which have also made possible progress in statistical investigations
into the causes of crime and what works to better prevent crime. We hope to shed more light onto crime patterns in L.A by adopting statistical analysis and visualisation tools, and using the results of our analysis to draw some conclusions on crime patterns in L.A that can be translated into policy initiatives. 



Data Description
=====================

The dataset contains information on crime incidents in Los Angeles. The source description (LAPD) states that the dataset may have some inaccuracies due to information being transferred from original crime statements that are typed on paper. As crime data contains sensitive personal information, fields that contain address information are only provided to the nearest hundred block. The dataset includes crime data from 2010 through September 2017.

Two separate csv files are provided with  Crime_Data_2010_2017  containing the main data and MO_Codes containing the description of MO codes that are included in the crime data for classification. 
The dataset is made up of 1.584.316 observations and 26 variables. To structure the variables, we split them into four groups: demographic, geographic, crime and time type variables. Demographic category consists of the victim’s age, sex and descent. The type of variables and a detailed description can be found in the table below: 

:Demographics

| Variable      |    Type     |   Description      |
| ------------- | ----------- | :---------------------------------------------------      |
| Victim.Age    |     dbl     |      Two character numeric   |
| Victim.Sex    |    fctr     |     F - Female M - Male X - Unknown  |
|Victim.Descent |    fctr     |      Descent Code: A - Other Asian B - Black C - Chinese D - Cambodian F - Filipino G - Guamanian H - Hispanic/Latin/Mexican I - American Indian/Alaskan Native J - Japanese K - Korean L - Laotian O - Other P - Pacific Islander S - Samoan U - Hawaiian V - Vietnamese W - White X - Unknown Z - Asian Indian    |



The geographical category contains variables relating to the geographical occurrence of crime and reporting of crimes. Variables include the area ID, the name of the area, the district reporting the crime, the premise code, a premise description, the address, the cross street of rounded address and the location where the crime occurred. The type of variables and a detailed description can be found in the table below: 

:Geographic

| Variable            |    Type     |   Description      |
| -------------       | ------------- | :-------------------------------------------------      |
| Area.ID             |  int    |  The LAPD has 21 Community Police Stations referred to as Geographic Areas within the department. These Geographic Areas are sequentially numbered from 1-21. |
| Area.Name           |  fctr    |   The 21 Geographic Areas or Patrol Divisions are also given a name designation that references a landmark or the surrounding community that it is responsible for. For example 77th Street Division is located at the intersection of South Broadway and 77th Street, serving neighborhoods in South Los Angeles.   |
| Reporting.District  |   int   |  A four-digit code that represents a sub-area within a Geographic Area. All crime records reference the "RD" that it occurred in for statistical comparisons.    |
| Premise.Code        | dbl     |  The type of structure, vehicle, or location where the crime took place.    |
| Premise.Description | fctr     |  Defines the Premise Code provided    |
| Address             |   fctr   |  Street address of crime incident rounded to the nearest hundred block to maintain anonymity.    |
| Cross.Street  |  fctr   | Cross Street of rounded Address.  |
| Location      |   fctr   |   The location where the crime incident occurred. Actual address is omitted for confidentiality. XY coordinates reflect the nearest 100 block.   |
             

The crime category contains all variables that describe the incidents of crime in more detail such as the type of crime, the weapons used or the current status of the crime. The variables we assorted to this category include the number of the crime on record, the weapons used and their description, the status of the crime (code and description), then crime codes and their description as well as the modus operandi associated with the suspect in commission of the crime.

:Crime

| Variable       |    Type     |   Description      |
| ------------- | -------------   | :------------------------------------------------------------------------      |
|  DR.Number        |      int   |    Division of Records Number: Official file number made up of a 2 digit year, area ID, and 5 digits       |
|  Weapon.Used.Code |     dbl    |   The type of weapon used in the crime.        |
|  Weapon.Description|  fctr     |    Defines the Weapon Used Code provided.       |
|  Status.Code      |   fctr     |    Status of the case. (IC is the default)       |
|  Status.Description|    fctr   |   Defines the Status Code provided.        |
|  Crime.Code.1     |    fctr    |    Indicates the crime committed. Crime Code 1 is the primary and most serious one. Crime Code 2, 3, and 4 are respectively less serious offenses. Lower crime class numbers are more serious.      |
|  Crime.Code.2     |    fctr    |  May contain a code for an additional crime, less serious than Crime Code 1.      |
|  Crime.Code.3     |    fctr    |    May contain a code for an additional crime, less serious than Crime Code 1.       |
|  Crime.Code.4     |    fctr    | May contain a code for an additional crime, less serious than Crime Code 1.          |
|  Crime.Code       |    int     |     Indicates the crime committed. (Same as Crime Code 1)      |
|  Crime.Code.Description|  fctr |   Defines the Crime Code provided.        |
|  MO.Codes         |   fctr     |     Modus Operandi: Activities associated with the suspect in commission of the crime.       |



The final category groups all variables related to time. It contains a variable that contains the reported date, the date and time occurrence.

:Time

| Variable      |    Type         |   Description  |
| ------------- | -------------   | :------------------------     |
| Date.Reported |     fctr     |   MM/DD/YYYY   |
| Date.Occurred |    fctr    |   MM/DD/YYYY   |
| Time.Occurred |      int     |    In 24 hour military time.   |



Data Cleaning Description
-------------------
As the data is provided in two different csv files. The first step that we took was to merge the crime_data and code_data into one single dataset. Then we looked at the date columns (date occured and date reported) and reformated each date to three new columns. Thus creating a new colum for the day occured, month occured and year occured as well as day reported, month reported and year reported. 
For the completeness of full information on every year, we have omitted data from the year 2017 and will focus on the data from 2010 to 2016 included. 

In order to make an interesting analysis we wanted to work with the information on victim descent. The abbreviations for victim descent in the original dataset, however, made analysis a little impractical as they weren't intuitively understandable (e.g. "D" standing for "Cambodian"). This is why we labeled the descent variables with the full description. (e.g. "W" being "White" and "D" being "Cambodian"). This led to ddd categories of descent: 

:Victim Descent

| Victim Descent Original  |   Victim Descent New  |
| ------------- | :------------------------     |
| H  |     Hispanic     | 
| W  |   White       | 
| B  |    Black      | 
| O  |   Other       | 
| A  |   Other Asian       | 
| C  |     Chinese     | 
| ' '  |          | 
| X  |    Unknown      | 
| F  |    Filipino      | 
| U  |   Hawaiian       | 
| K  |    Korean      | 
| P  |   Pacific Islander       | 
| G  |    Guamanian      | 
| J  |   Japanese       | 
| I  |    American Indian/Alaskan Native      | 
| V  |   Vietnamese       | 
| Z  |    Asian Indian      | 
| S  |    Samoan      | 
| D  |    Cambodian      | 
| L  |    Laotian      | 
| -  |    -      | 

As there were some very specific subcategories for America (such as Alaskan Native)  we also added an additional more global colum on victim descent to be able to work with both the more detailed descent information and the more global descent variables. We reduced the global descent column to contain six groups(White, Black, Hispanic, Other, Asian and Pacific.  

In order to simplify the mapping of location information, we also extracted longitude and latitude from the location column and created additional, separate columns for longitude and latitude. 

The data covers the 21 different areas of Los Angeles and categorizes 135 different types of crimes.
--> renamed crime variables 



Demographic
=====================

_Text here_

Age and sex distribution
-------------------

```{r library, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(ggmap)
library(ggplot2)
library(dplyr)
library(lubridate)
library(tidyr)
library(stringr)
library(scales)

```

```{r , echo=FALSE}

##distribution of age among all victims
summary(crime_data$Victim.Age,na.rm=TRUE)
ggplot(crime_data,aes(x=Victim.Age,na.rm=TRUE))+geom_density()

#can choose either one below(haven't decided yet)
#plot option 1:
crime_data%>%filter(Victim.Sex=="F"|Victim.Sex=="M")%>%
ggplot(aes(x=Victim.Age,fill=Victim.Sex)) + geom_histogram(binwidth = 1,position="dodge")

```
The summary of the victim age shows the youngest victim is only 10 years old and the oldest being 99 years old.The mean age of victim is around 36 years old.From the density plot of victim age,we can see that there are two peak points at 
14 and 25 respectively.In addition,a histogram plot of the victim age of male and female is shown above.From the overlapping pattern,it is obvious that male are more likely to be a victim of crime at a young age(10-15 years old) or from 40 to 70 years old while female tend to be more in danger between around 15 to 35 years old,especially aged between 18 and 25.For example,at age 25,number of female victims are approximately 7500 higher than male victims.

```{r}
#summary of female age and male age respectively
female_age<-crime_data$Victim.Age[crime_data$Victim.Sex=="F"]
male_age<-crime_data$Victim.Age[crime_data$Victim.Sex=="M"]
summary(female_age,na.rm=TRUE)
summary(male_age,na.rm=TRUE)

```
_Hypothesis testing_
```{r , echo=FALSE}
# Code here
t.test(female_age,male_age,alternative = "two.sided")

```
_Text here_
From the summary of both male and female,the mean age of victim is lower for female(37.52 years old).We want to see whether this difference in mean age is due to random variation.A t-test is conducted to find out the results.Based on the t-test,we can conclude that there is strong evidence in rejecting the null hypothesis that the difference in means is 0.Thus,mean age of victim is significantly smaller for female.




Ethnicity
-------------------


```{r , echo=FALSE}
#average age of victims based on ethnicity and gender(Hispanic has the lowerst avg age)
avg_age<-crime_data%>%
  group_by(Victim.Descent.Global,Victim.Sex)%>%
  filter(!is.na(Victim.Age),!Victim.Descent.Global=="-",!Victim.Descent.Global=="",
         Victim.Sex=="F"|Victim.Sex=="M")%>%
  summarise(avg_age=mean(Victim.Age),count=n())%>%
  arrange(avg_age)

#option1:barchart of mean age between different Ethnicity
ggplot(avg_age,aes(x=Victim.Descent.Global,y=avg_age,fill=Victim.Sex))+geom_bar(stat = 'identity', position = 'dodge')+labs(x="race of victim",y="average age of victim")

#option2:boxplot of age between different Ethnicity
crime_data%>%
  filter(Victim.Sex=="F"|Victim.Sex=="M",!Victim.Descent.Global=="-",!Victim.Descent.Global=="")%>%
  ggplot(aes(x=Victim.Sex,y=Victim.Age,fill=Victim.Descent.Global))+geom_boxplot()
```
From the bar chart of average victim age based on ethnicity and gender,Hispanic have the lowest average age among all ethnicity groups and female Hispanic is the lowest(around 33 years old).For Blacks and Hispanic,female victim tends to be younger on average while it is not that obvious for other ethinicty groups.We want to carry out hypothesis testing to determine whether it is indeed the case according to the plot.

```{r}
#number of vitims with different gender and ethnicity
crime_data%>%
  filter(Victim.Sex=="F"|Victim.Sex=="M",!Victim.Descent.Global=="-",!Victim.Descent.Global=="")%>%
  ggplot(aes(x=Victim.Age,fill=Victim.Sex,  na.rm=TRUE)) + geom_bar()+facet_wrap(~Victim.Descent.Global)+
  labs(x="Victime Age",y="Number of victims")
```
From the above plot,it is obvious that Hispanic account for the largest part of victims and we would like to focus on Hispanic victims.


```{r}
#Thus focus on Hispanic
demographic <- crime_data %>% select(Victim.Age, Victim.Descent.Global, Victim.Sex) %>% 
 filter( !is.na(Victim.Age),!Victim.Descent.Global=="-",!Victim.Descent.Global=="",
         Victim.Sex=="F"|Victim.Sex=="M")%>%
  group_by(Victim.Age, Victim.Descent.Global, Victim.Sex) %>% 
  summarise(count = n())

Hispanic <- filter(demographic,  Victim.Descent.Global== "Hispanic")

ggplot(Hispanic, aes(x = Victim.Age, y = count, fill = as.factor(Victim.Sex))) + 
  geom_bar(stat = 'identity', position = 'dodge')    
```

_Text here_
We now have some clue in the most likely victim of a crime:Hispanic young female aged aroung 25 years old.
_Hypothesis testing_

```{r}
Hispanic_female1<-crime_data%>%filter(Victim.Descent.Global=="Hispanic")
Hispanic_female<-Hispanic_female1$Victim.Age[Hispanic_female1$Victim.Sex=="F"]
Hispanic_male1<-crime_data%>%filter(Victim.Descent.Global=="Hispanic")
Hispanic_male<-Hispanic_male1$Victim.Age[Hispanic_male1$Victim.Sex=="M"]
t.test(Hispanic_female,Hispanic_male,alternative = "two.sided")

black_female1<-crime_data%>%filter(Victim.Descent.Global=="Black")
black_female<-black_female1$Victim.Age[black_female1$Victim.Sex=="F"]
black_male1<-crime_data%>%filter(Victim.Descent.Global=="Black")
black_male<-black_male1$Victim.Age[black_male1$Victim.Sex=="M"]
t.test(black_female,black_male,alternative = "two.sided")

white_female1<-crime_data%>%filter(Victim.Descent.Global=="White")
white_female<-white_female1$Victim.Age[white_female1$Victim.Sex=="F"]
white_male1<-crime_data%>%filter(Victim.Descent.Global=="White")
white_male<-white_male1$Victim.Age[white_male1$Victim.Sex=="M"]
t.test(white_female,white_male,alternative = "two.sided")


```
From the t-tests above,female Hispanic victims are around 6 years younger on average than male Hispanic victims.For black people,female victims are around 3 years younger on average than male victims.However,as for white people,the average age is approximately the same(with a difference of between 0.02 to 0.25).

```{r , echo=FALSE}
# Code here
#
crime_data1<-filter(crime_data,!crime_data$Victim.Descent=="")
sum(crime_data1$Victim.Descent.Global=="White")/nrow(crime_data1)
sum(crime_data1$Victim.Descent.Global=="Black")/nrow(crime_data1)
sum(crime_data1$Victim.Descent.Global=="Hispanic")/nrow(crime_data1)

```
We did a proportion comparison with real population data.According to the population of LA,white people was 49.8% while black people was 9.6% of the population.While in the crime data,white people was 27.4% and black people was 17.8%.Thus,there are huge difference between the population proportion with the crime proportion. 




Correlation between type of crime and age/sex/ethnicity (PLOT + hypothesis Testing !)
-------------------


relationship with type of crime
-------------------
```{r , echo=FALSE}
#type of crime with gender
type<-crime_data%>%select(crime_type,Victim.Sex,Victim.Age)%>%
  filter(!is.na(Victim.Age), Victim.Sex=="F"|Victim.Sex=="M")%>%
  group_by(crime_type,Victim.Sex)%>%
summarise(count=n())%>%
  arrange(desc(count))
ggplot(type, aes(x =crime_type , y= count,fill=Victim.Sex)) + geom_bar(position = position_dodge(),stat = 'identity')  +
  theme(axis.text = element_text(angle= 45, hjust = 1))+labs(x="crime type",y="number of victims")+scale_y_continuous(breaks=c(10000,20000,40000,80000,100000,200000,300000))
```
From the barplot on crime type above,burglary,battery,assault and vandalism are the most likely crime types.Burglary and assault tends to be aiming more on male while battery and other sexual offences have more female victims.

```{r}
#boxplot of victim age between different type of crimes and gender
crime_data%>%
  filter(Victim.Sex=="F"|Victim.Sex=="M",!Victim.Descent.Global=="-",!Victim.Descent.Global=="")%>%
  group_by(crime_type,Victim.Sex)%>%
  
  ggplot(aes(x=Victim.Sex,y=Victim.Age,fill=crime_type))+geom_boxplot()

```
Type of crime and ethnicity
-------------------
```{r}
crime_data %>% filter(!Victim.Descent.Global=="-",!Victim.Descent.Global==" ") %>% ggplot(aes(x=Victim.Descent.Global, fill=crime_type))+ geom_bar(position='fill') + labs(x="Victim's Ethnicity", y= "Proportion of Crimes")
```

We next look at the type of crimes that happen to different ethnic groups, more specifically, what proportion of victims from each ethnic group belong to each type of crime. We find that black victims are more likely to be victims of assault and battery compared to the other ethnic groups and burglary/theft is the most common crime for all ethnic groups. Also, the proportion of victims that are victims of burglary/theft is lower than the other ethnic groups. 


Area distribution
=====================

We have seen who are the victims of the crime, now let's focus on the location of these crimes. Of course, we can make the hypothesis that the location depends on the type of crime and on the victim.

number of crimes in different areas
-------------------

First, we want to study the distribution of crime in the different areas.

```{r , echo=FALSE}
top5_crime <-  crime_data %>% select(Area.Name, crime_type) %>% group_by(crime_type, Area.Name) %>% summarise(count = n()) %>% top_n(5, wt =  count) 
top5_crime

ggplot(crime_data, aes(x = crime_type)) + geom_bar() + facet_wrap(~ Area.Name) + theme(axis.text = element_text(angle= 60, hjust = 1))
```

From these graphs, we can see that the distribution of the type of crime is slightly similar in the different areas. 

_Hypothesis testing_

Let's conduct a X-squared test to test the hypothesis whether the crime area is independent of the type of a crime at .05 significance level.

```{r}
tbl = table(crime_data$Area.Name, crime_data$crime_type) 
chisq.test(tbl)
```

As the p-value is lower than the .05 significance level, we reject the null hypothesis that the crime area is independent of the type of a crime.

Hence, let's delve deeper into the analysis to see the correlation between these two variables.



Let's study more specificaly the distribution of crime between 77th Street and SouthWest.

```{r}

crime_data_77_SW <- crime_data %>% select(Area.Name, crime_type) %>% filter(Area.Name == 'Topanga' | Area.Name == 'Hollenbeck')
crime_data_77_SW$Area.Name <- sapply(crime_data_77_SW$Area.Name, as.character)
crime_data_77_SW$crime_type <- sapply(crime_data_77_SW$crime_type, as.character)
test <- chisq.test(table(crime_data_77_SW$Area.Name, crime_data_77_SW$crime_type))
table(crime_data_77_SW$Area.Name, crime_data_77_SW$crime_type)
test
```



Another way to address the problem is to look at the crime density for different type of crime in Los Angeles.


Area distrubution per type of crime 
-------------------

```{r, fig.width=7, fig.height=10}

crime_data_coord <- crime_data %>% select(longitude, lattitude, Year.Occurred, crime_type) %>% filter(Year.Occurred == 2016)


LAMap <- ggmap(
  get_map("Los Angeles", zoom = 11), extent = "device", 
  legend = "topright")

LAMap +
  stat_density2d(aes(x = longitude, y = lattitude, fill = ..level.., 
                     alpha = ..level..),
    size = 2, bins = 4, data = crime_data_coord, geom = "polygon", na.rm = TRUE) +
  scale_fill_gradient("Crime\nDensity") +
  scale_alpha(range = c(.4, .8), guide = FALSE) +
  guides(fill = guide_colorbar(barwidth = 1, barheight = 6)) + facet_wrap( ~ crime_type)
```


Premise of a crime scene per sex
-------------------


for the main areas with highest crime rate - what are the main types of crime


Time
=====================

_Text here_

Day Time according to type of crime
-------------------

(ex : fraud in the day, rape a night, burglary during the day etc...)

```{r , echo=FALSE}
# Code here
```

_Text here_

_Hypothesis testing_

```{r , echo=FALSE}
# Code here
```

Day Time according to sex
-------------------

```{r , echo=FALSE}
# Code here
```

_Text here_

_Hypothesis testing_

```{r , echo=FALSE}
# Code here
```

Correlation between time reported - time occured and type of crime
-------------------

```{r , echo=FALSE}
# Code here
```

_Text here_

_Hypothesis testing_

```{r , echo=FALSE}
# Code here
```

Correlation between time reported - time occured and case solved or not for a specific month
-------------------

```{r , echo=FALSE}
# Code here
```

_Text here_

_Hypothesis testing_

```{r , echo=FALSE}
# Code here
```


Public holidays impact
-------------------

Effect of Public Holidays on crime Occurrence and Type.
```{r}

#Exploratory plot
ggplot(crime_data,aes(x=Date.Occurred.C,color=public_holiday))+geom_bar()+scale_color_manual(values=c("red","blue"))

crime_data%>%
  group_by(public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(public_holiday) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(desc(average.crime.per.day))


crime_data%>%
  filter(Day.Occurred=="01" & Month.Occurred=="01") %>%
  group_by(Date.Occurred.C) %>%
  summarise(count=n())
    
crime_data%>%
  group_by(Jan1=ifelse(Day.Occurred=="01" & Month.Occurred=="01",TRUE,FALSE))%>%
  summarise(Average.Report.Time=mean(Time.Between.Occured.Reported)) %>%
  arrange(desc(Average.Report.Time))


crime_data%>%
  filter(Day.Occurred!="01" & Month.Occurred!="01")%>%
  summarise(Occured.Reported.Gap.SD=sd(Time.Between.Occured.Reported))

```

Findings from the exploratory plot and tables:
i.) The mean of # of crime in LA is higher on public holidays, but
ii.) The number of crime is significantly higher on 1st of Jan in every year, and
iii.) The length between occured time and reporting time tend to be longer on 1st Jan in every year;


I cannot find information regarding this on the dataLA website, but it looks like they have coded crime incidents occured on other days as 1st Jan for some conditions.
So should we exclude cases with reporting time lag for say i.)365 days/ ii. 15 days (which is the average)?


As nature of Sundays is similar to holidays, I will include all Sundays as 'public holidays and Sundays' as the next step.




```{R}
#exclude lagged for more than 15 days (15 or 15+71 (1SD) or 15 + 141 (2SD?)

crime_data$Jan1.exclude.15 <- crime_data$Day.Occurred=="01" & crime_data$Month.Occurred=="01" & crime_data$Time.Between.Occured.Reported>15


crime_data%>%
  filter(Jan1.exclude.15==FALSE)%>%
  group_by(public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(public_holiday) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(desc(public_holiday))

#by crime type
crime_data%>%
  filter(Jan1.exclude.15==FALSE)%>%
  group_by(crime_type,public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(crime_type,public_holiday) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(crime_type,desc(public_holiday))

```


Included Sundays and exclude crime occured on 1st Jan and have a time gap between occured and report >15 days

```{R}


crime_data%>%
  filter(Jan1.exclude.15==FALSE)%>%
  group_by(Sundays_public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(Sundays_public_holiday) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(desc(Sundays_public_holiday))

#by crime type
crime_data%>%
  filter(Jan1.exclude.15==FALSE)%>%
  group_by(crime_type,Sundays_public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(crime_type,Sundays_public_holiday) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(crime_type,desc(Sundays_public_holiday))

```


```{r}
#two sample t-test - is there a difference between # of crime on public holidays/Sundays vs other days?

Regular_day_crime <- crime_data%>%filter(Sundays_public_holiday==FALSE & Jan1.exclude.15==FALSE)%>%select(Date.Occurred.C)%>%
  group_by(Date.Occurred.C)%>%summarise(count=n())

Holiday_crime <- crime_data%>%filter(Sundays_public_holiday==TRUE & Jan1.exclude.15==FALSE)%>%select(Date.Occurred.C)%>%
  group_by(Date.Occurred.C)%>%summarise(count=n())

mean(Regular_day_crime$count); mean(Holiday_crime$count)

t.test(Regular_day_crime$count,Holiday_crime$count,alternative = "greater")

```


Result shows that the average number of crime on holidays and Sundays is lower than that in regular days in 95% significance level.


```{r}
#By crime type (Chi-sq-test?)
crime_data_excluded_1Jan_15 <- crime_data%>%filter(Jan1.exclude.15==FALSE) %>% select(crime_type,Sundays_public_holiday,Date.Occurred.C) %>% group_by(crime_type,Sundays_public_holiday,Date.Occurred.C) %>% summarise (countperday=n()) %>% ungroup() %>% group_by(crime_type,Sundays_public_holiday) %>% summarise (average_per_day=mean(countperday))

crime_data_excluded_1Jan_15

PH_Crimetype_tbl <- xtabs(average_per_day~crime_type+Sundays_public_holiday,crime_data_excluded_1Jan_15)
PH_Crimetype_tbl
```

Most of crime type has less ocuuring rate on public holidays, but it likes look assault, battery, gunshots, rape and vandalism has a higher occuring rate in public holidays.


Prediction and logistic regression
=====================

_Data Cleaning_

```{r}
# Remove missing values for victim age and premise code
crime_data[, "Victim.Sex"] <- sapply(crime_data[, "Victim.Sex"], as.character)
crime_data_NA <- crime_data[!is.na(crime_data$Victim.Age) & !is.na(crime_data$Premise.Code) & (crime_data$Victim.Sex == "F" | crime_data$Victim.Sex == "M"),]
crime_data[, "Victim.Sex"] <- sapply(crime_data[, "Victim.Sex"], as.factor)

```

_Training set and learning set_

```{r}
train_data <- crime_data_NA[crime_data_NA$Year.Occurred != 2016, ]
test_data <- crime_data_NA[crime_data_NA$Year.Occurred == 2016, ]
```

_Predict the type of crime_

First, we try to predict the type of crime according to different parameters such as the age of the potential victim, the sex, the ethnicity and the area

```{r}
#Multinomial Logistic Regression

library("nnet")
library(pscl)

model <- multinom(Area.Name ~ Victim.Age + Victim.Sex + Victim.Descent +  crime_type, data = test_data)

summary <- summary(model)

pR2(model)

test_data_predict <- test_data %>% select(Victim.Age, Victim.Sex, crime_type)
predict_area <- predict(model, test_data_predict, type = 'class')

sum(test_data$Area.Name == predict_area)/length(predict_area)

```


Discussion
=====================

What results did you find?	
-------------------

Why is this interesting?
-------------------

Help LA police, predict the crime, prevention for the potential victims

What would be the next steps?	
-------------------




