---
title: "Final Report"
author: "Group B"
date: "September 29, 2017"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
    fig_width: 7
    fig_height: 6
    fig_caption: true
    df_print: tibble
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
\newpage

Introduction
=====================

_Text here_

Context
-------------------
_Text here_

Theory
-------------------
_Text here_


Data Description
=====================

Text here


| Titre 1       |     Titre 2     |   Titre 3      |
| ------------- | -------------   | ---------      |
| Colonne       |     Colonne     |      Colonne   |
| Alignée à     |      Alignée au |     Alignée à  |
| Gauche        |      Centre     |      Droite    |


Demographic
=====================

_Text here_

Age and sex distribution
-------------------

```{r , echo=FALSE}
# Code here
```

_Text here_

_Hypothesis testing_
```{r , echo=FALSE}
# Code here
```

_Text here_

Ethnicity
-------------------

```{r , echo=FALSE}
# Code here
```

_Text here_

_Hypothesis testing_

```{r , echo=FALSE}
# Code here
```

_Text here_


Correlation between type of crime and age/sex/ethnicity (PLOT + hypothesis Testing !)
-------------------

Area distribution
=====================

_Text here_

number of crimes in different areas per sex
-------------------

```{r , echo=FALSE}
# Code here
```

_Text here_

_Hypothesis testing_

```{r , echo=FALSE}
# Code here
```

Area distrubution per type of crime 
-------------------

```{r , echo=FALSE}
# Code here
```

_Text here_
Correlation between area and type of crime (hypothesis testing)

_Hypothesis testing_

```{r , echo=FALSE}
# Code here
```

Premise of a crime scene per sex
-------------------


for the main areas with highest crime rate - what are the main types of crime


Time
=====================

_Text here_

Day Time according to type of crime
-------------------

(ex : fraud in the day, rape a night, burglary during the day etc...)

```{r , echo=FALSE}
# Code here
```

_Text here_

_Hypothesis testing_

```{r , echo=FALSE}
# Code here
```

Day Time according to sex
-------------------

```{r , echo=FALSE}
# Code here
```

_Text here_

_Hypothesis testing_

```{r , echo=FALSE}
# Code here
```

Correlation between time reported - time occured and type of crime
-------------------

```{r , echo=FALSE}
# Code here
```

_Text here_

_Hypothesis testing_

```{r , echo=FALSE}
# Code here
```

Correlation between time reported - time occured and case solved or not for a specific month
-------------------

```{r , echo=FALSE}
# Code here
```

_Text here_

_Hypothesis testing_

```{r , echo=FALSE}
# Code here
```


Public holidays impact
-------------------

```{r , echo=FALSE}
# Code here
```

_Text here_

_Hypothesis testing_

```{r , echo=FALSE}
# Code here
```


Prediction and logistic regression
=====================



Discussion
=====================

What results did you find?	
-------------------

Why is this interesting?
-------------------

Help LA police, predict the crime, prevention for the potential victims

What would be the next steps?	
-------------------



