---
title: "PublicHolidays"
author: "Sepp"
date: "29 September, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#Import packages
library(dplyr)
library(ggmap)
library(ggplot2)
library(dplyr)
library(lubridate)
library(tidyr)
library(stringr)


#Read Data
#crime_data <- read.csv("data/clean_data.csv")

```


Effect of Public Holidays on crime Occurrence and Type.
```{r}

#Exploratory plot
ggplot(crime_data,aes(x=Date.Occurred.C,color=public_holiday))+geom_bar()+scale_color_manual(values=c("red","blue"))

crime_data%>%
  group_by(public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(public_holiday) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(desc(average.crime.per.day))


crime_data%>%
  filter(Day.Occurred=="01" & Month.Occurred=="01") %>%
  group_by(Date.Occurred.C) %>%
  summarise(count=n())
    
crime_data%>%
  group_by(Jan1=ifelse(Day.Occurred=="01" & Month.Occurred=="01",TRUE,FALSE))%>%
  summarise(Average.Report.Time=mean(Time.Between.Occured.Reported)) %>%
  arrange(desc(Average.Report.Time))


crime_data%>%
  filter(Day.Occurred!="01" & Month.Occurred!="01")%>%
  summarise(Occured.Reported.Gap.SD=sd(Time.Between.Occured.Reported))

#ggplot(crime_data[(crime_data$Day.Occurred!="01" & crime_data$Month.Occurred!="01"),],aes(x=Time.Between.Occured.Reported))+geom_bar()

```
Findings from the exploratory plot and tables:
i.) The mean of # of crime in LA is higher on public holidays, but
ii.) The number of crime is significantly higher on 1st of Jan in every year, and
iii.) The length between occured time and reporting time tend to be longer on 1st Jan in every year;


I cannot find information regarding this on the dataLA website, but it looks like they have coded crime incidents occured on other days as 1st Jan for some conditions.
So should we exclude cases with reporting time lag for say i.)365 days/ ii. 15 days (which is the average)?


As nature of Sundays is similar to holidays, I will include all Sundays as 'public holidays and Sundays' as the next step.


```{R}

# included Sundays

#Exploratory plot
ggplot(crime_data,aes(x=Date.Occurred.C,color=Sundays_public_holiday))+geom_bar()+scale_color_manual(values=c("red","blue"))

crime_data%>%
  group_by(Sundays_public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(Sundays_public_holiday) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(desc(average.crime.per.day))



# Only Sundays

crime_data%>%
  group_by(Sundays,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(Sundays) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(desc(average.crime.per.day))




#### conclusion, not to group Sundays and PHs/// revised, to include PHs as PHs usually have less crime per day

```


```{R}
#exclude lagged for more than 1 year




crime_data$Jan1.exclude.365 <- crime_data$Day.Occurred=="01" & crime_data$Month.Occurred=="01" & crime_data$Time.Between.Occured.Reported>365

crime_data%>%
  filter(Jan1.exclude.365==FALSE)%>%
  group_by(public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(public_holiday) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(desc(public_holiday))

#by crime type
crime_data%>%
  filter(Jan1.exclude.365==FALSE)%>%
  group_by(crime_type,public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(crime_type,public_holiday) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(crime_type,desc(public_holiday))

#exclude lagged for more than 15 days (15 or 15+71 (1SD) or 15 + 141 (2SD?)

crime_data$Jan1.exclude.15 <- crime_data$Day.Occurred=="01" & crime_data$Month.Occurred=="01" & crime_data$Time.Between.Occured.Reported>15


crime_data%>%
  filter(Jan1.exclude.15==FALSE)%>%
  group_by(public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(public_holiday) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(desc(public_holiday))

#by crime type
crime_data%>%
  filter(Jan1.exclude.15==FALSE)%>%
  group_by(crime_type,public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(crime_type,public_holiday) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(crime_type,desc(public_holiday))



```


Included Sundays

```{R}

crime_data%>%
  filter(Jan1.exclude.365==FALSE)%>%
  group_by(Sundays_public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(Sundays_public_holiday) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(desc(Sundays_public_holiday))

#by crime type
crime_data%>%
  filter(Jan1.exclude.365==FALSE)%>%
  group_by(crime_type,Sundays_public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(crime_type,Sundays_public_holiday) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(crime_type,desc(Sundays_public_holiday))


crime_data%>%
  filter(Jan1.exclude.15==FALSE)%>%
  group_by(Sundays_public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(Sundays_public_holiday) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(desc(Sundays_public_holiday))

#by crime type
crime_data%>%
  filter(Jan1.exclude.15==FALSE)%>%
  group_by(crime_type,Sundays_public_holiday,Date.Occurred.C)%>%
  summarise(count=n()) %>%
  group_by(crime_type,Sundays_public_holiday) %>%
  summarise(average.crime.per.day=mean(count)) %>%
  arrange(crime_type,desc(Sundays_public_holiday))

```

```{R}
# Please ignore the code below.
crime_data%>%
  filter(long.report.time==TRUE) %>%
  group_by(Date.Occurred.C)%>%
  summarise(count=n())%>%
  arrange(desc(count))

crime_data_holidays <- filter(crime_data,public_holiday==TRUE)

crime_data_holidays <- mutate(crime_data_holidays,long.report.time=ifelse(Time.Between.Occured.Reported>365,TRUE,FALSE))


crime_data_holidays%>%
  filter(long.report.time==TRUE) %>%
  group_by(Date.Occurred.C)%>%
  summarise(count=n())%>%
  arrange(desc(count))



```

